---
title: "dh_edges2nodes"
author: "Pozdniakov"
date: '22.04.2017'
output: html_document
---

#Libraries  

```{r libs}
library("data.table") #rather popular "R dialect" for easy and efficient data wrapping. Alternative to dplyr package
library("igraph") #the most popular package for working with graphs
#library("networkD3") #graph visualisation using D3.js library for JavaScript
```

#Introduction  

We calculate [betweeness centrality]()(BC), [closeness centrality](https://en.wikipedia.org/wiki/Closeness_centrality)(CC), [strength(=weighted degree)](https://arxiv.org/pdf/cond-mat/0311416.pdf)(S), [degree](https://en.wikipedia.org/wiki/Degree_(graph_theory))(D), and average distance (as 1/CC). All these measurements (except for strength) ignore weights.  

For statistics we calculate max and average degree, graph density, mean and max path length (based on average distance) for every file.  

#Preparation  

You need to set some parameters first:  

+ You need to specify `path` variable - full path to folder with csvs  

+ project name (it will be used for names of output files `full` and `stats`); by default, it is the input folder name  

+ `output` folder (by default is `path/CSVproject`)  

Please, check that your csvs have these columns (order is important!):  

1. Source  
2. Type  
3. Source
4. Weight  

All other columns will be ignored.

```{r path}
path <-  "C:/Users/BucHe/Documents/GitHub/RusDraCor/TEI/current_CSV_files_extracted_from_TEI/ilibrary"
project <- NA
output <- NA
```

```{r some stuff}
project <- ifelse(is.na(project), project <- gsub(".*/([^/\\])/?", "\\1", path), project)
output <- ifelse(is.na(output), file.path(path, paste0("CSV",project)), output)
dir.create(output)
big <- data.table() #creating empty variable for binding
files <- list.files(path = path, pattern = ".*\\.csv")
```

#Your files  

There are `r length(files)` .csv files in `r path` folder. 

Ok, let's start `r project`. 

#Main script

```{r csv to data.table}
csv2d <- function(file){
d <- fread(file, encoding = "UTF-8")
d <- d[,c(1,3,2,4)] #changing columns order
colnames(d) <- tolower(colnames(d))
d <- d[weight>0,]
d}
```

```{r data.table to igraph}
d2ig <- function(d){
x <- graph_from_data_frame(d, directed = F)
V(x)$betweenness <- betweenness(x, v = V(x), directed = F, weights = NA)
V(x)$closeness <- closeness(x, weights = NA)
V(x)$strength <- strength(x)
V(x)$degree <- degree(x)
V(x)$average_distance <- 1/closeness(x, weights = NA)
V(x)$graph_density <- edge_density(x)
x
}
```

```{r write new vertices csv}
ig2csv <- function (x, file){
  xdf <- as.data.table(as_data_frame(x, "vertices"))
  write.csv2(xdf, file = file.path(output,file))
  xdf
}
```


```{r main}
convert <- function(filename){
  tryCatch({
ig <- d2ig(csv2d(file = file.path(path, filename)))
if (length(ig[]) == 0) return(sprintf("Empty file: %s; the file is skipped", filename))
namenew <- gsub("(.*)(\\.csv)", "\\1_vertices\\2", filename)
big <<- rbind(big, ig2csv(ig, namenew)[,file:=filename][,author:=gsub("([^_]*)_(.*)", "\\1", filename)])
#print(plotnet(ig2d3(ig)))
sprintf("Processed successfully: %s",filename)
}, error = function(e)  sprintf("Error!!! with: %s; the file is skipped", filename)
  )
}
```

```{r batch converting}
lapply(files, convert)
```

```{r statistics table}
stats <- big[, .(max_degree = max(degree), 
                average_degree = mean(degree), 
                density = mean(graph_density),
                average_path_length = mean(average_distance), 
                max_path_length = max(average_distance)),
             by = .(author,file)]
```


```{r writing summary tables}
write.csv2(big, file = file.path(output, paste0("full_", project,".csv")))
write.csv2(stats, file = file.path(output, paste0("stats_",project,".csv")))
```



```{r visualization, eval=FALSE, include=FALSE}
ig2d3 <- function(x, cluster = cluster_label_prop, edgesize = 0.05, nodesize = 0.01){
members <- membership(cluster(x))
x_d3 <- igraph_to_networkD3(x, group = members)
x_d3$links$value = E(x)$weight*edgesize
x_d3$nodes$nodesize = V(x)$strength*nodesize
x_d3
}

plotnet <- function(x_d3, charge = -1000){forceNetwork(Links = x_d3$links, Nodes = x_d3$nodes, charge = -1000, Source = 'source', Target = 'target', NodeID = 'name', Group = "group", Value = "value", Nodesize = "nodesize", opacityNoHover = 0.8)}
```


```{r plotting, eval=FALSE, include=FALSE}

#for (i in files){

  #print(i)
  #print(plotnet(ig2d3(d2ig(csv2d(file.path(path, i))))))

  #}
```

```{r, eval=FALSE, include=FALSE}

#for (i in files){
#print(plotnet(ig2d3(d2ig(csv2d(file.path(path, i))))))
#}
#lapply(files, function (x) print(plotnet(ig2d3(d2ig(csv2d(file.path(path, x)))))))
```

```{r, eval=FALSE, include=FALSE}


#b <- ig2csv(d2ig(csv2d(file.path(path, "Ostrovskij_Groza.csv"))), "mjfjf.csv")
#convert(files[2])
```

