---
title: "Drama Analysis"
author: "Ira Pavlova"
date: "May 2017"
output:
  github_document:
    html_preview: false
---

## This project is devoted to studying the evolution of Russian drama. The study is based on the Russian Drama Corpus which now contains 49 Russian plays encoded in TEI. The creation time of plays ranges from 1747 to 1925.
```{r results='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(plotly)
library(plotrix)
library(network)
library(sna)
library(GGally)
library(geomnet)
library(ggnetwork)
library(igraph)
library(tools)
library(gridExtra)

data = read.csv('calculations.csv', stringsAsFactors=FALSE)
data = data.frame(data)
data[data=="empty weights"] <- 0
data[, 5:6] <- sapply(data[, 5:6], as.numeric)
data
```

## This graph shows how the distribution of number of segments (act/scenes) in plays from 1750 to 1950. 
```{r}
data %>% ggplot(aes(Year_of_creation, Num_of_scenes)) +
  geom_point(size=0.2) +geom_text(aes(label=Play),hjust=0, vjust=0, size=1.5) +
  scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  labs(title='Number of scenes/acts in Russian drama',
       y='Number of segments', x='Year of creation')
```

## This graph shows how the distribution of number of segments (act/scenes) in plays from 1750 to 1950 for three different genres -- comedy, tragedy and drama. 
```{r warning=FALSE, message=FALSE}
subset(data, Genre=='comedy' | Genre=='tragedy' | Genre=='drama') %>% ggplot(aes(Year_of_creation, Num_of_scenes)) +
  geom_point(aes(color=Genre), size=2) + stat_ellipse(geom = "polygon", alpha=0.1, aes(color=Genre, fill=Genre)) +
  scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  labs(title='Number of scenes/acts in Russian drama depending on genre',
       y='Number of segments', x='Year of creation')
```

## This graph shows how the number of characters in plays was changing from 1750 to 1950.
```{r}
BG <- subset(data, Play == "Pushkin_-_Boris_Godunov")
GT <- subset(data, Play == "Gogol_Teatralnyi_razezd_posle_predstavlenija_novoi_komedii")
GT1 <- subset(data, Play == "Gogol'_-_Teatral'nyj_raz'ezd_posle_predstavlenija_novoj_komedii")
SG <- subset(data, Play == "Ostrovskij_Snegurochka")

data %>% ggplot(aes(Year_of_creation, Num_of_char)) +
  geom_smooth(method='lm', color='black') +
  geom_point() + scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  geom_text(data=BG, label="Boris Godunov", vjust=1, size=3) +
  geom_text(data=GT, label="Teatralnyi razezd posle predstavlenija novoi komedii", vjust=1, size=3) +
  geom_text(data=GT1, label="Teatralnyi razezd posle predstavlenija novoi komedii", vjust=1, size=3) +
  geom_text(data=SG, label="Snegurochka", vjust=1, size=3) +
  labs(title='Number of characters in Russian drama',
       y='Number of characters', x='Year of creation')

```

However, this graph does not tell us much except the variaty of plays and absolute outliers. Maybe if we had around 300 plays we would see some stable development. As collecting the bigger corpus is work in progress, let's take a closer look at plays with more than 4 segments (act/scenes), exploring the distribution of number of characters for different groups of plays depending on the number of segments in these plays.

## This graph shows how the number of characters in plays was changing from 1750 to 1950 for the plays with 4/10/20/30 or more segments.
```{r}

char_data_4 <- subset(data, Num_of_scenes >= 4)

char_data_4 <- ggplot(char_data_4, aes(Year_of_creation, Num_of_char, label=Play)) +
  geom_point(size=0.2) + scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  geom_text(aes(label=Play),hjust=0, vjust=0, size=1.5) +
  labs(title='in plays of 4 and more segments',
       y='Number of characters', x='Year of creation')

char_data_10 <- subset(data, Num_of_scenes >= 10)

char_data_10 <- ggplot(char_data_10, aes(Year_of_creation, Num_of_char, label=Play)) +
  geom_point(size=0.2) + scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  geom_text(aes(label=Play),hjust=0, vjust=0, size=1.5) +
  labs(title='in plays of 10 and more segments',
       y='Number of characters', x='Year of creation')

char_data_20 <- subset(data, Num_of_scenes >= 20)

char_data_20 <- ggplot(char_data_20, aes(Year_of_creation, Num_of_char, label=Play)) +
  geom_point(size=0.2) + scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  geom_text(aes(label=Play),hjust=0, vjust=0, size=1.5) +
  labs(title='in plays of 20 and more segments',
       y='Number of characters', x='Year of creation')

char_data_30 <- subset(data, Num_of_scenes >= 30)

char_data_30 <- ggplot(char_data_30, aes(Year_of_creation, Num_of_char, label=Play)) +
  geom_point(size=0.2) + scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  geom_text(aes(label=Play),hjust=0, vjust=0, size=1.5) +
  labs(title='in plays of 30 and more segments',
       y='Number of characters', x='Year of creation')

grid.arrange(char_data_4,
              char_data_10,
              char_data_20,
              char_data_30,
              nrow=2, ncol=2,
             top="Number of charaters in Russian drama")

```

## This graph shows how the number of characters in plays was changing from 1750 to 1950 for three different genres -- comedy, tragedy and drama.
```{r warning=FALSE, message=FALSE}
subset(data, Genre=='comedy' | Genre=='tragedy' | Genre=='drama') %>% ggplot(aes(Year_of_creation, Num_of_char)) +
  geom_point(aes(color=Genre), size=2) + stat_ellipse(geom = "polygon", alpha=0.1, aes(color=Genre, fill=Genre)) +
  scale_x_continuous(breaks=seq(1700, 1950, 50)) +
  labs(title='Number of characters in Russian drama',
       y='Number of characters', x='Year of creation')
```

## Setting directories for CSV files to generate network graphs
```{r}
csv_list_ilibrary <- list.files('../TEI/current_CSV_files_extracted_from_TEI/ilibrary', full.names=T, pattern = "\\.csv$")

csv_list_wikisource <- list.files('../TEI/current_CSV_files_extracted_from_TEI/wikisource', full.names=T, pattern = "\\.csv$")

csv_list_test <- list.files('../Calculating_stuff_in_plays/test_csvs', full.names=T, pattern = "\\.csv$")
```

```{r echo=FALSE}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

## Making network visualization (ggplot) -- basic "easy" graphs
```{r echo=FALSE}
make_ggplot_graphs <- function(input){
  
            output <- file_path_sans_ext(basename(file.path(input)))
            print(output)
            play <- read.csv(input, sep = ";")
            num_of_rows <- nrow(play)
            if(num_of_rows != 0)
            {
            play <- play[, c(1, 3, 4)]
            play
            
            ggplot(data = play, aes(from_id=Source, to_id=Target)) +
              geom_net(layout.alg ="kamadakawai", 
              size = 2, labelon = TRUE, vjust = -0.6, ecolour = "grey60",
              directed =FALSE, fontsize = 3, ealpha = 0.5) +
              labs(title=output)
            
            print(ggplot(data = play, aes(from_id=Source, to_id=Target)) +
              geom_net(layout.alg ="kamadakawai", 
              size = 2, labelon = TRUE, vjust = -0.6, ecolour = "grey60",
              directed =FALSE, fontsize = 3, ealpha = 0.5) +
              labs(title=output))

            ggsave(paste(output,".png"),
                   path= '../Calculating_stuff_in_plays/network_graphs/ggplot')
            
  } else {print('empty graph')}}

par(mfrow = c(7, 10)) 
for(file in csv_list_ilibrary) make_ggplot_graphs(file)
for(file in csv_list_wikisource) make_ggplot_graphs(file)

```

## Making network visualization (igraph) with characters clustering
```{r echo=FALSE}
make_igraph_graphs <- function(input)
  {
            output <- file_path_sans_ext(basename(file.path(input)))
            print(output)
            play <- read.csv(input, sep=";")
            num_of_rows <- nrow(play)
            if(num_of_rows != 0)
            {
              play <- play[, c(1, 3, 4)]
            play
net <- graph_from_data_frame(d=play, directed=F)
E(net)$weight <- play$Weight
# net <- network(play, directed=FALSE)

clust <- cluster_optimal(net)

V(net)$community <- membership(clust)

prettyColors <- c("slategray2", "rosybrown1", "palevioletred2","plum", "seagreen3", "mistyrose1", "lightsalmon1")
communityColors <- prettyColors[membership(clust)]
V(net)$color <- prettyColors[membership(clust)]

#layout=layout.fruchterman.reingold(net)

layout=layout.kamada.kawai(net, kkconst=50)


E(net)$color <- apply(as.data.frame(get.edgelist(net)), 1,
                      function(x) ifelse(V(net)$community[x[1]] == V(net)$community[x[2]], 
                                   V(net)$community[x[1]], '#00000000'))
# print(V(net)$community)
# print(E(net)$color)

# vertex.label= ifelse(V(net)$name %in% c('Drugoj'),V(net)$name, NA)

filename= paste('../Calculating_stuff_in_plays/network_graphs/igraph/', output, '.png', sep='')

print(plot(net,
     vertex.size=10,
     edge.arrow.size=.6,
     edge.color='lightsteelblue',
     vertex.label=V(net)$name,
     edge.width=E(net)$weight*0.3,
     layout=layout.graphopt,
     vertex.label.color="black",
     vertex.label.cex=0.3,
     vertex.label.dist=0.8,
     vertex.label.family="Helvetica",
     vertex.label.font=2
     ))
title(output, cex.main=0.7)

png(filename, width=3.25,height=3.25, units='in', res=600)

plot(net,
     vertex.size=10,
     edge.arrow.size=.6,
     edge.color='lightsteelblue',
     vertex.label=V(net)$name,
     edge.width=E(net)$weight*0.3,
     layout=layout.graphopt,
     vertex.label.color="black",
     vertex.label.cex=0.3,
     vertex.label.dist=0.8,
     vertex.label.family="Helvetica",
     vertex.label.font=2
     )
title(output, cex.main=0.7)
     
dev.off() }
            else {print('empty graph')
}}

#for(file in csv_list_test) make_igraph_graphs(file)

for(file in csv_list_ilibrary) make_igraph_graphs(file)
for(file in csv_list_wikisource) make_igraph_graphs(file)

```

## In progress:
# Calculating degree for every charecter and plotting vertex size by degree.
# Improving graph appearance.
# Figuring out how to plot all the networks graphs on a single plot.
# Introducing more detailed analysis for authors and genres differencies.